### 2014-12-04 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report and temperature color bars

>>>>

The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were injured after making entry to the first floor and had to either bail out through a window or be rescued. From Section~\ref{temp}, the conditions on the first floor were initially tenable. After the front door was opened, however, the simulation results indicate that a high hazard area existed in the first floor that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.

The simulation results indicate that a flow path was established between the basement and front side of the structure (through the front door of the first floor) after the front door was opened. Strong winds (8.9~m/s (20~mph)) pushed air into the rear basement through window failures combined with boyant combustion gases pressurized the structure. Opening the front door provided a pressure relief; this resulted in a rapid change in the conditions within the flow path. After the front door was opened, the combustion gases at elevated temperature and pressure in the basement  flowed towards lower pressure regions outside of the structure on the leeward side (front of structure) via the interior stairwell. The two firefighters were located in the flow path on first floor between the top of the interior stairwell and the front door.
